pema application

### 2022-12-05 paper/manuscript.Rmd
fixed typos

<span id = "earlierpapers">Some seminal studies have applied the LASSO to perform moderator selection in meta-regression [@rosettieCosteffectivenessHPVVaccination2021; @sebriNaturalResourcesIncome2021; @requiaGlobalAssociationAir2018].
This suggests that others have recognized its potential for exploring heterogeneity when the number of moderators is relatively high to the number of studies.
However, these existing publications have taken a two-step approach, whereby moderators are first selected using LASSO regression,
and selected moderators are then included in meta-regression analysis.
This approach is fraught; firstly, because of known problems of inference after variable selection [@zhangInferenceVariableSelection1992].
As the moderators included in the second step are based on an exploratory first step,
their parameters are not valid for inference.
Secondly, although the LASSO model in the first step accounts for potential multicollinearity by including all colinear variables but restricting the size of their coefficients,
the meta-regression in the second step no longer does so.
A three-step extension of the two-step approach exists
that uses principles from the causal inference literature to overcome these limitations [@belloniInferenceTreatmentEffects2014].
BRMA, by contrast, overcomes these limitations by introducing a one-step approach that performs inference within the penalized framework.</span>

@@

A regularizing prior distribution shrinks small coefficients towards zero by assigning high probability mass to near-zero values.
There are many different regularizing prior distributions,
some of which are analogous to specific frequentist methods [@vanErpOberskiMulder2019].
For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].
Both the the frequentist LASSO penalty and the Bayesian LASSO prior have a tuning parameter $\lambda$ that controls the amount of regularization.
In frequentist LASSO, its value is usually chosen via cross-validation [@hastieElementsStatisticalLearning2009]. 
In the Bayesian approach, by contrast,
its value can be optimized during model estimation.

>>>>

<span id = "earlierpapers">Some seminal studies have applied the LASSO to perform moderator selection in meta-regression [@rosettieCosteffectivenessHPVVaccination2021; @sebriNaturalResourcesIncome2021; @requiaGlobalAssociationAir2018].
This suggests that others have recognized its potential for exploring heterogeneity when the number of moderators is relatively high to the number of studies.
However, these existing publications have taken a two-step approach, whereby moderators are first selected using LASSO regression,
and selected moderators are then included in meta-regression analysis.
This approach is fraught; firstly, because of known problems of inference after variable selection [@zhangInferenceVariableSelection1992].
As the moderators included in the second step are based on an exploratory first step,
their parameters are not valid for inference.
Secondly, although the LASSO model in the first step accounts for potential multicollinearity by including all collinear variables but restricting the size of their coefficients,
the meta-regression in the second step no longer does so.
A three-step extension of the two-step approach exists
that uses principles from the causal inference literature to overcome these limitations [@belloniInferenceTreatmentEffects2014].
BRMA, by contrast, overcomes these limitations by introducing a one-step approach that performs inference within the penalized framework.</span>

@@

A regularizing prior distribution shrinks small coefficients towards zero by assigning high probability mass to near-zero values.
There are many different regularizing prior distributions,
some of which are analogous to specific frequentist methods [@vanErpOberskiMulder2019].
For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].
Both the frequentist LASSO penalty and the Bayesian LASSO prior have a tuning parameter $\lambda$ that controls the amount of regularization.
In frequentist LASSO, its value is usually chosen via cross-validation [@hastieElementsStatisticalLearning2009]. 
In the Bayesian approach, by contrast,
its value can be optimized during model estimation.
